null_model

### 2020-09-15 analysis/ts_null_model.Rmd
read in null samples and process into table

>>>>

Create Null table
```{r}
path <- here::here("data", "fd_null_output")
null_files <-  dir(path, "*.csv") %>%
  paste0(path, "/", .)

process_nulls <- function(file_path){
  data <- read_tsv(file_path) %>%
    mutate(plot_id = as.character(plot_id)) %>%
    select(year, plot_id, richness = nbsp, everything(), -sing.sp, -starts_with("CWM"), -n) %>%
    group_by(year)

  means <- data %>%
    select(-plot_id, -richness) %>%
    summarise(across(everything(), mean)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "mean")

  sds <- data %>%
    select(-plot_id, -richness) %>%
    summarise(across(everything(), sd)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "sd")

  stats <- left_join(means, sds, by = c("year", "metric")) %>%
    left_join(data %>% select(year, plot_id, richness) %>% distinct(), by = "year") %>%
    mutate(se = sd/sqrt(n),
           lowerCI = mean - qt(0.975, n - 1) * se, 
           upperCI = mean + qt(0.975, n - 1) * se)  %>%
    select(year, plot_id, everything())

  return(stats)
}

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls)

usethis::use_data(null_table)
pins::pin(null_table, board = "github")
```
